---
title: "Semiconductor Demand"
description: |
  Semiconductor demand in the past 35 years.
author:
  - name: Alex Kuai
date: "`r Sys.Date()`"
output: distill::distill_article
bibliography: bibliography.bib
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(tidyverse)
library(janitor)
library(httr)
library(rvest)
library(readxl)
library(plotly)
library(DT)
library(rmarkdown)
market_data <- read_rds("rawdata.rds")
```

### Raw Data
This is the raw data from the original xls file downloaded from the website. 

```{r raw data display}
raw_data <- read_xls("API_NY.GDP.PCAP.CD_DS2_en_excel_v2_4250700.xls")
paged_table(raw_data)
  # try to find out how to display this as a clean dataset with pages and everything
```
Looking at this, it isn't pretty. The years are in the same column as the countries, column names are all messed up do to how this was formatted; so then it was time to wrangle it into place. 

### Wrangling
Scanning through the data, it was clear that we needed to first change the names of these columns, because they were all messed up.

Furthermore, the countries column has the years in it. That isn't right. So we need a new column to hold the years, then delete all of the ones from where they aren't supposed to be. 

After polishing this dataset into something usable, here it is!

```{r finished_data_display}
read_rds("rawdata.rds")
```


### Semiconductor Demand From Four Regions
Historical billings of semiconductor demand from the Americas, the Asia Pacific, Europe, and Japan are shown here. 

```{r demand_plot}
market_graph <- market_data |> 
  ggplot(aes(x = year, y = Total_Year, fill = Regions, color = Regions,
             text = paste("Year:", year, "\n", 
                          "Demand:", Total_Year, "m"))) +
  geom_point(alpha = .5) +
  facet_wrap(~Regions) +
  theme_classic() +
  theme(legend.position = "none") +
  labs(title = "Semiconductor Demand 1986 to 2021",
       x = "Year",
       y = "Total Semiconductor Demand (millions)")
ggplotly(market_graph, tooltip = "text")
```
[@Billings_Report]

There is massive growth in semiconductor demand in the Asia Pacific Region, peaking at almost 343 million semiconductor units reported to be purchased. 

The semiconductor demand in the Americas have steadily increased, but nowhere near the growth of the Asia Pacific region. 

Demand for semiconductors in Europe and Japan have been relatively low, and there haven't been any particularly high amounts of growth demand for them either. 





