---
title: "Country growth"
description: |
  This section is focusing on a country's technological growth.
author:
  - name: Alex Kuai
date: "`r Sys.Date()`"
output: distill::distill_article
bibliography: bibliography.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(rvest)
library(janitor)
library(tidyverse)
library(readxl)
plot_data <- read_rds("growth.rds")
```

### Raw Data
The raw data for this graph is here.

```{r}
read_xls("API_SP.POP.TOTL_DS2_en_excel_v2_4250716.xls")
```

Here is the polished version and the end product it created. 

```{r data_plotting}
plot_data
plot_data |> 
  ggplot(aes(x = year, y = population, fill = region, color = region)) +
  geom_point(alpha = 0.5) +
  facet_wrap(~region) +
  labs(title = "Population of Four Regions",
       subtitle = "The Asia Pacific region has the highest population growth",
       x = "Year",
       y = "Population(millions)",
       caption = "The World Bank") +
  theme(legend.position = "none")
```
[@Population_Report]

### Conclusion
We can see that in this graph, just like the semiconductor demand graph, had the Asia Pacific Region leading in population growth, and the other countries trailing behind, and perhaps this is because of improved living conditions due to an influx of microchips.


